An agent-based model for city networks based on interactions between firms

### 2019-11-12 main.tex

@@

% We compare the model to real data on transnational firm networks defined by ownership links at city-level, by the means of the Bureau Van Dijk's \emph {FAME} database with a graph theory application.

@@

@@

@@

More probably, we may have to work on an extract of the AMADEUS database including only links from and to UK-based companies. This constraints imposes modifications on the level to remain consistent:
\begin{itemize}
    \item the adjustment error can only be partial and computed on the UK links only
    \item an initialization method for the missing links must be implemented (e.g. through a statistical analysis? not far from the model then)
    \item the model can be run without initial links, and an additional parameter sets the duration necessary to reach the time considered as the first date
\end{itemize}

@@

@@

% On vine copulas :
%    https://link.springer.com/article/10.1023/A:1016725902970
%    https://www.groups.ma.tum.de/en/statistics/research/vine-copula-models/
%    R package : https://github.com/tnagler/VineCopula

@@

%%%%%%%%%%%%%
\begin{figure}
    \includegraphics[width=0.48\textwidth]{figures/ex_alleq-highgravity_seed-12102_t1500.png}\hspace{0.1cm}
    \includegraphics[width=0.48\textwidth]{figures/ex_alleq-lowgravity_seed-12102_t1500.png}	
    \caption{Example of simulated networks at $t=1500$, with a high (resp. low) gravity decay parameter on the left (resp. right).\label{fig:example}}
\end{figure}
%%%%%%%%%%%%%

@@

\begin{figure}
	\includegraphics[width=0.48\textwidth]{figures/internationalization-gravityDecay_errorbars.png}
    \includegraphics[width=0.48\textwidth]{figures/rhoDegreeSize-gravityDecay_errorbars.png}\\

\end{figure}

@@

>>>>

% possible target JOEG? https://academic.oup.com/joeg/

@@

\cite{martinus2019brokerage} role of small countries

\cite{dawley2019creating} regional policies for insertion in global network

\cite{turkina2016structure} networks of industrial clusters

\cite{gluckler2016relational} positioning within networks

We compare the model to real data on transnational firm networks defined by ownership links at city-level, by the means of the Bureau Van Dijk's \emph {FAME} database with a graph theory application.

@@

% stats to describe the structure of the database, nb of total links, nodes, missing values? + nb of firms per country,  total turnover generated per country etc..

@@

\subsection{Network analysis}

% - network properties of European network (FUAs) in time -> centralities (! directed links), weighted in/out degree

% - correlation with city size etc (check indics of the simulation model?)

% - correlation FUAs gdp from ucdb / gdp by aggregating firms

@@

%%%
% with new dataset we do not have a subsample of companies within a specific country anymore
%More probably, we may have to work on an extract of the AMADEUS database including only links from and to UK-based companies. This constraints imposes modifications on the level to remain consistent:
%\begin{itemize}
%    \item the adjustment error can only be partial and computed on the UK links only
%    \item an initialization method for the missing links must be implemented (e.g. through a statistical analysis? not far from the model then)
%    \item the model can be run without initial links, and an additional parameter sets the duration necessary to reach the time considered as the first date
%\end{itemize}

@@

\begin{table}
    \caption{List of parameters, associated processes, and ranges.}
    \begin{center}
    \begin{tabular}{|c|c|c|c|}
    \hline
    Parameter & Name & Process & Range \\\hline
      $\gamma_F$ & Origin &  & $\left[0;10\right]$ \\
    $\gamma_T$ & Destination & & $\left[0;10\right]$ \\
    $\gamma_W$ & Previous links & Self-reinforcement & $\left[0;10\right]$  \\
    $\gamma_D = \frac{1}{d_G}$ & Geographical distance & & $\left[0;10000\right]$ \\
    $\gamma_G  = \frac{1}{d_G}$ & Socio-cultural distance & & $\left[0;10000\right]$ \\\hline
    \end{tabular}
    \end{center}
\end{table}

@@

% On vine copulas :
%    https://link.springer.com/article/10.1023/A:1016725902970
%    https://www.groups.ma.tum.de/en/statistics/research/vine-copula-models/
%    R package : https://github.com/tnagler/VineCopula
% Q: what would be the meaning on parametrizing interaction function with a real Vine copula? non-linear interactions? (on log, linear combination of factors)

@@

%%%%%%%%%%%%%
\begin{figure}
    \includegraphics[width=0.48\textwidth]{figures/ex_alleq-highgravity_seed-12102_t1500.png}
    \includegraphics[width=0.48\textwidth]{figures/ex_alleq-lowgravity_seed-12102_t1500.png}	
    \caption{Example of simulated networks at $t=1500$, with a high (resp. low) gravity decay parameter on the left (resp. right).\label{fig:example}}
\end{figure}
%%%%%%%%%%%%%

\cite{railsback2017improving} netlogo perfs

@@

\begin{figure}
	\includegraphics[width=0.48\textwidth]{figures/internationalization-gravityDecay_errorbars.png}
    \includegraphics[width=0.48\textwidth]{figures/rhoDegreeSize-gravityDecay_errorbars.png}
    \caption{(Left) Internationalization index decreases exponentially with gravity decay; (Right) Correlation between city weighted degree and size. Both plots show a transition from a local to a global regime.}
\end{figure}

\begin{figure}
    \includegraphics[width=0.48\textwidth]{figures/internationalization-gammaSectors_errorbars.png}
    \includegraphics[width=0.48\textwidth]{figures/rhoDegreeSize-gammaSectors_errorbars.png}
    \caption{(Left) Internationalization varies linearly with sector proximity $\gamma_S$; (Right) Correlation between degree and size exhibits a maximum, witnessing an intermediate regime where size is the most important}
\end{figure}

\paragraph{Grid exploration}

\begin{figure}
    \includegraphics[width=\textwidth]{figures/internationalization_countryGravityDecay200_gammaDestination0_facetwrapgammaOrigin_colorgammaSectors.png}
    \caption{The transition as a function of interaction range depends on the influence of origin size $\gamma_F$; sector proximity $\gamma_S$ plays a role only for a large influence of the origin.}
\end{figure}

\begin{figure}
    \includegraphics[height=0.6\textheight]{figures/networkAvgCommunitySize_countryGravityDecay2100_gammaDestination0_facetwrapgammaOrigin_colorgammaSectors.png}
	\caption{Maximal integration in term of community size is achieved at an intermediate value of $d_G$: emergence of a regional regime; Maximal size depends on the role of sectors $\gamma_S$, in a decreasing way when origin size is deactivated, and increasing way when $\gamma_F=1$; This regime disappear when origin size influence is too large}
\end{figure}

@@

%%%%%%%%%%%%%%%
\section{Discussion}

% - evolution of city sizes (co-evolution model)

% - role of path dependency

% - towards a model with firm agents? (multi-scale ABM)
